Software reliability: Experiences\\ in European scientific research\\ projects and new trends

### 2017-11-08 paper.tex
remove sloc

The ETICS \cite{cordis:etics} and ETICS 2 \cite{cordis:etics2} (Jan 2006 -- Feb 2010) projects aimed at defining and implementing a framework able to integrate a combination of new technologies in test management, release management tools and resource virtualization to improve quality, reliability and interoperability of large--scale scientific software. Both projects supported mechanisms to measure static software metrics (such as Lines of Code (LOC), Source LOC (SLOC), and Complexity); to measure the number of faults, the number of defects, number of bugs; execute unit testing; deploy and test software on a virtual set of resources \cite{etics}. The {\sl ETICS} portal was the first automated service for delivering software products in distributed environments such as the Grid.

>>>>

The ETICS \cite{cordis:etics} and ETICS 2 \cite{cordis:etics2} (Jan 2006 -- Feb 2010) projects aimed at defining and implementing a framework able to integrate a combination of new technologies in test management, release management tools and resource virtualization to improve quality, reliability and interoperability of large--scale scientific software. Both projects supported mechanisms to measure static software metrics, number of faults, number of defects and number of bugs; execute unit testing; deploy and test software on a virtual set of resources \cite{etics}. The {\sl ETICS} portal was the first automated service for delivering software products in distributed environments such as the Grid.
